Cultural Evolution of Conservation Behavior at the Intersection of Working

### 2020-11-11 DissertationProposal/DissertationProposal.Rmd
added good map. Should probably actually use this in the earlier intro part?

### Methodological Specifics
I will map all the seeded and voluntarily copied fuel-efficient cookstoves in Makangale, Msituu mkuu, and Kifundi (aka Before Ningeze Forest) wards on Pemba Island, Tanzania (Fig \@ref(fig:mapp)). With the assistance of a translator, I will survey all the individuals responsible for constructing each cookstove, measure a suite of physical characteristics of each cookstove (length, height, etc.), and measure the fuel efficiency.

```{r mapp, echo=FALSE, fig.cap="Satellite map of Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "75%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/BadPembaMap.png")
```

>>>>

### Methodological Specifics
I will map all the seeded and voluntarily copied fuel-efficient cookstoves in Makangale, Msituu mkuu, and Kifundi wards on Pemba Island, Tanzania (Fig \@ref(fig:mapp)). With the assistance of a translator, I will survey all the individuals responsible for constructing each cookstove, measure a suite of physical characteristics of each cookstove (length, height, etc.), and measure the fuel efficiency.

```{r mapp, echo=FALSE, fig.cap="Satellite map of Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "75%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/MapLines.png")
```
